% E. Dunham -- Resume
% Contents Copyright (C) 2014 - 2016, E. Dunham

% LaTeX code for rendering the resume is distributed under the MIT license.
% See LICENSE.txt. It means you can use the code for whatever you want,
% including your own resume, but I'm not liable if it catches your computer on
% fire.

% Template originally developed by E. Dunham
% https://github.com/edunham/resume/blob/master/resume.tex

\documentclass[11pt]{article} % Set default font size to 11pt


% Some settings that the stuff hidden in the preamble will reference
\def \whitespaciness { 0 } % pt. bigger numbers = emptier page. 0 is ok.
\def \typeoffill {\dotfill} % hfill makes blank, dotfill makes dotted lines.


\input{preamble}
\begin{document}

\centerline{{\Huge \bf Jorge E. Barsoba}}

\bigskip

\contact{jebarsoba@gmail.com}
        {jebarsoba.github.io}
        {github.com/jebarsoba}
        {Buenos Aires, Argentina \& Remote}

\heading{Skills}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\skill{Fundamentals}
      {Data structures and algorithms, OOP, TDD, SOLID}

\skill{Programming languages}
      {JavaScript, C\#, HTML, CSS}

\skill{Frameworks}
      {Node.JS, Angular, .NET Framework}

\skill{Platforms}
      {Kubernetes (AKS), AWS API Gateway / Lambda (Serverless), IIS}

\skill{Databases}
      {MongoDB, AWS ElastiCache (Redis) and DynamoDB, SQL Server}

\skill{Tools}
      {Git, TFS, Sumo Logic}

\heading{Employment}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{sovanta AG}
           {Senior Software Engineer}
           {02/2019 - Present}

Working for multiple customer-facing projects, as a Frontend, Backend or Fullstack developer, according to demand needs.
\vskip 0.1in
Projects (Role | App type | Industry | Technology):
\begin{itemize}
\item Fullstack | Web | Pharmaceuticals | Angular, Redux, Node.JS, MySQL (TypeORM)
\item Fullstack | Web / Mobile (iOS) | Automotive | OpenUI5, Cordova, Node.JS, MongoDB (Mongoose), Kubernetes (AKS), Firebase (Push notifications)
\item Frontend | Web | Beverages | AngularJS (1.x)
\item Backend | Chatbot (Web / Mobile) | Retailing | Node.JS, MongoDB (Mongoose), Kubernetes (AKS), Dialogflow, SAP Conversational AI
\end{itemize}

\experience{Accenture}
           {Software Developer - Associate Manager}
           {12/2018 - 02/2019}

\experience{Accenture}
           {Software Developer - Specialist}
           {10/2015 - 12/2018}

\begin{itemize}
\item Rewrote in Node.JS/JavaScript a critical .NET/C\# backend service, and migrated it from IaaS to an AWS Lambda based PaaS, without interrupting operations.
\item Integrated SAP IdM and Microsoft Dynamics by developing a custom interface using Rhino/JavaScript and OData when SAP did not offer a connector out-of-the-box.
\item Improved the performance of a webapp by implementing ElastiCache and ASP.NET tweaks, leading to a 60\% reduction in page load times and a decrease in backend workloads.
\item Developed SAP Gateway OData services using ABAP to go-live in less than four months, without any prior ABAP experience.
\item Integrated SalesForce and SAP Finance by leveraging Azure Service Bus and developing an NServiceBus endpoint that handles 12K messages every day.
\end{itemize}

\experience{Grupo Santillana}
           {Software Development Team Lead}
           {08/2009 - 10/2015}

- Led the group of developers who built a BPM solution to digitize critical business processes of the publishing group.

- Contributed to the implementation of the Scrum agile framework, playing the role of ScrumMaster.

- Guided the adoption of software engineering practices such as TDD and Continuous Integration.

\end{description}

\heading{Academics}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Universidad Tecnológica Nacional}
           {Systems Engineering}
           {Graduated on 07/2015}

- As the final project of my 5-year degree, developed an Android application that brings together story telling for kids and voice recognition.

\end{description}

\heading{Recent Speaking Engagements}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\squish

\event{ATAG Summit}
      {04/2018}
      {}
      {An error handling strategy to reduce money loss}

\hfill \small ...more at https://jebarsoba.github.io/2018/04/20/error-handling.html

\end{document}
